Checking Big Suffix and LCP Arrays by Probabilistic Methods

### 2017-03-30 draft-new/draft.tex
2017/03/30

Algorithm~\ref{alg:1} performs multiple scans and sorts on the arrays of $\mathcal{O}(n)$ fixed-size tuples in disks. Given RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}. Algorithm~\ref{alg:1} reaches its peak disk use when sorting the tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}. Suppose the input string and the suffix/LCP array are encoded as $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is a $\gamma$-byte integer, it takes $(2 \cdot (\alpha +2 \cdot \beta))$ space for sorting the tuples of $ST_1/ST_1'$ and $(2 \cdot (\alpha + 2 \cdot \beta + \gamma))$ for sorting the tuples of $ST_2/ST_2'$ and $ST_3/ST_3'$. For saving space, our program implementing the algorithm tackles $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the fingerprints, using less space but more time. The experiment in Section~\ref{sec:experiment} indicates that {\color{red}{the disk use is 40 times the size of $x$.}}

@@

From our perspective, a checker should be not only fast but also general. For program debugging, we usually check the output of a builder by comparing it with that of another builder. But this is not feasible in all the cases, for example, an algorithm for constructing infinite-order array can not be directly used to check a finite-order array and vise versa. On the contrary, our first method can be generalized to check the correctness of the lexical order and the LCP values of any pairs of suffixes. This makes it possible for verifying any full or sparse suffix/LCP array of any order.

>>>>

Algorithm~\ref{alg:1} performs multiple scans and sorts on the arrays of $\mathcal{O}(n)$ fixed-size tuples in disks. Given RAM size $M$, disk size $D$ and block size $B$, all are in words, the time and I/O complexities for each scan are $\mathcal{O}(n)$ and $\mathcal{O}(n / B)$, respectively, while those for each sort are $\mathcal{O}(n\log_{M/ B}(n / B))$ and $\mathcal{O}((n / B)\log_{M / B}(n / B))$, respectively~\cite{Arge2013}. Algorithm~\ref{alg:1} reaches its peak disk use when sorting the tuples in lines~\ref{alg:1:b} and~\ref{alg:1:e}. Suppose the input string and the suffix/LCP array are encoded as $\alpha$- and $\beta$-byte integers, respectively, and each fingerprint is a $\gamma$-byte integer, it takes $(\alpha +2 \cdot \beta)$ space for sorting the tuples of $ST_1/ST_1'$ and $(\alpha + 2 \cdot \beta + \gamma)$ for sorting the tuples of $ST_2/ST_2'$ and $ST_3/ST_3'$. For saving space, our program implementing the algorithm tackles $ST_1/ST_1'$, $ST_2/ST_2'$ and $ST_3/ST_3'$ separately and performs a single scan over $x$ for each of them to obtain the fingerprints, using less space but more time. The experiment in Section~\ref{sec:experiment} indicates that {\color{red}{the disk use is 40 times the size of $x$.}}

@@

From our perspective, a checker should be not only fast but also general. %For program debugging,
{\color{red}{In practice,} \color{blue}{not only for program debugging but also for checking results from probabilistic builders}} we usually check the output of a builder by comparing it with that of another builder. But this is not feasible in all the cases, for example, an algorithm for constructing {\color{red}{an}} infinite-order array can not be directly used to check a finite-order array and vise versa. On the contrary, our first method can be generalized to check the correctness of the lexical order and the LCP values of any pairs of suffixes. This makes it possible for verifying any full or sparse suffix/LCP array of any order.
